SHARP - II. Mass structure in strong lenses is not necessarily dark matter substructure: A flux ratio anomaly from an edge-on disc in B1555+375

### 2016-06-22 papers/B1555_EdgeOn/B1555_letter.tex
update paper minor typo

The next step is to test if a physically plausible edge-on disc can cause a perturbation in the strong lensing mass model that produces the observed flux ratio anomaly of  merging images A and B. \textbf{Our model contains a SIE plus an exponential disc component (SIE+ExpDisc) due to that  exponential disc profile matches the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$). A detailed definition of these mass profiles is described by \citet{Kee01}. The source position adds two additional model parameters. 
%We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
%An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.}

@@

\begin{figure*}
\includegraphics[width=0.9\textwidth]{b1555_3panel.eps}
\caption{
{\bf (a)} $K^\prime$-band AO imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here (blue) overlaid.
%
{\bf (b)} $K^\prime$-band AO image with the locations of the four radio components
marked with circles.  
%
{\bf (c)} Observed radio (blue pluses) and model-predicted (red open
circles) image positions of B1555+375. The lens-plane critical curves
are shown with the blue solid line and the source-plane caustics are
shown with the red dotted line. The position of the source is at
($-0.1953$, $-0.1494$), which is marked by the red filled circle. The
centroid positions of the two mass components of the lens (a SIE and
an exponential disc) are marked by the black filled triangles.
}
\label{fig:3panel}
\end{figure*}

>>>>

The next step is to test if a physically plausible edge-on disc can cause a perturbation in the strong lensing mass model that produces the observed flux ratio anomaly of  merging images A and B. \textbf{Our model contains a SIE plus an exponential disc component (SIE+ExpDisc) due to that  exponential disc profile matches the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).\textbf{ A detailed definition of these mass profiles is described by \citet{Kee01} eq. (73) \& (74) .} The source position adds two additional model parameters. 
%We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
%An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.}

@@

\begin{figure*}
\includegraphics[width=0.9\textwidth]{b1555_3panel_new.eps}
\caption{
{\bf (a)} $K^\prime$-band AO imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here (blue) overlaid.
%
{\bf (b)} $K^\prime$-band AO image with the locations of the four radio components
marked with circles.  
%
{\bf (c)} Observed radio position: blue pluses. Model-predicted position: red open
circles. The lens-plane critical curves
are shown with the blue solid line and the source-plane caustics are
shown with the red dotted line. The position of the source is at
($-0.1953$, $-0.1494$), which is marked by the red filled circle. The
centroid positions of the SIE and ExpDisc components of the lens are marked by the black and red filled triangles respectively. The disc middle plane measured with NICMOS image is shown with the black dashed line.
}
\label{fig:3panel}
\end{figure*}
